---
title: "Data Import"
author: "Yuanqing Jiang"
date: "4/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. What function would you use to read a file where fields were separated with “|”?
```{r eval=FALSE}
read_delim(file, delim = "|")
```

### 2. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?
```{r eval=FALSE}
intersect(names(formals(read_csv)), names(formals(read_tsv)))
```

### 3. What are the most important arguments to read_fwf()?
```{r eval=FALSE}
fwf_widths() 
fwf_positions()
```
### 4. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?

```{r eval=FALSE}
#"x,y\n1,'a,b'"

read_delim("x,y\n1,'a,b'",
           ",", quote = "'")
read_csv("x,y\n1,'a,b'",
         quote = "'")
```

### 5. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?
```{r eval=FALSE}
read_csv("a,b\n1,2,3\n4,5,6")
#Warning: parsing failures
#The first vector has different amount of elements from the secound vector and the third vector.

read_csv("a,b,c\n1,2\n1,2,3,4")
#Warning: parsing failures
#The three vectors have different amount of elements.

read_csv("a,b\n\"1")
#Warning: parsing failures
#Data content in not clear. The second line only includes 1 element.

read_csv("a,b\n1,2\na,b")
#Nothing's wrong with this line of code.

read_csv("a;b\n1;3")
#This data is ; dilimited, so use read_csv2 is a better choice.
read_csv2("a;b\n1;3")
```
